%
% My Resume - Revisions/Overhaul (V2)
% written by Ian Lulu
% © 2023-2024
%
% To do: 
% - [ ] add icons to links?
% - [ ] add colors?
% - [ ] bullet points on top to 6 point stars?
%
% Sources: https://youtu.be/VjsX4tznW40?si=vSv164aqXVxFtoIG
% Useful resources: https://linktr.ee/chrisjr404, https://ecc.uic.edu/career-tools/resume/, https://photos.app.goo.gl/bEvNLQvJcdg6JeEc6
%                   https://www.businessinsider.com/resume-mistakes-looking-for-jobs-overseas-india-australia-interview-recruitment-2024-3?utm_source=copy-link&utm_medium=referral&utm_content=topbar#amp_tf=From%20%251%24s&aoh=17098285428335&csi=0&referrer=https%3A%2F%2Fwww.google.com&ampshare=https%3A%2F%2Fwww.businessinsider.com%2Fresume-mistakes-looking-for-jobs-overseas-india-australia-interview-recruitment-2024-3
%

\documentclass{article}


% preamble (?) edit: code to ensure pdf output will be unicode and machine-readable
% source: https://www.reddit.com/r/LaTeX/comments/3nr2vn/how_can_i_ensure_that_my_latex_resume_is_readable/
\input{glyphtounicode}
\pdfgentounicode=1


\usepackage{titlesec}
\usepackage{titling}
\usepackage[margin=0.25in]{geometry}
\usepackage{hyperref}


\titleformat{\section}
{\vspace{-4pt}\scshape\bfseries\Large} % 1st argument: formatting - \scshape = small caps text but it no worky for some reason 🤔🧐💭🤨
{} % numbering
{0em} % indentation between numbering and text(?)
{} % more stuff before the title but after the numbering(?not sure abt this one as well)
[{\titlerule[1pt]}\vspace{-4pt}] % to have a line under the thing you're formatting, in this case sections


\titleformat{\subsection}
{\bfseries\large}
{}
{0em}
{}


\titleformat{\subsubsection}[runin]
{\bfseries}
{$\bullet$}
{0.5em}
{}


\titlespacing{\subsubsection}
{0em} % left margin
{0em} % space before section(??)
{0em} % space after section(?)


\renewcommand{\maketitle}{
    \begin{center}
    {\bfseries\huge
    %\theauthor
    Ian Lulu}
    
    \vspace{0.25em}

    (708) 315-9423 {$\ast$} \href{mailto:ianpatricklulu@gmail.com}{\underline{ianpatricklulu@gmail.com}} {$\ast$} \href{https://www.linkedin.com/in/ianlulu/}{\underline{LinkedIn}} {$\ast$} \href{https://github.com/IanLulu}{\underline{GitHub}} {$\ast$} \url{ianlulu.me}
    
    \end{center}
}


% made a command to make the in-built \romannumeral into uppercase
\newcommand{\RomanNumeralCaps}[1]
    {\MakeUppercase{\romannumeral #1}}


\begin{document}


\title{R\'esum\'e}
\author{Ian Patrick Amal Lulu}


\maketitle
\pagenumbering{gobble} % turns off page numbering (turkey lol)


\section{Summary}
Computer Science graduate with strong technical and engineering skills in information technology and software engineering.
Possesses over two years of hands-on work and research experience, working with computer networking and software development among others.
Passionate about learning and thrive on working in high-impact projects.


\section{Education}
% \subsection{University of Illinois Chicago (UIC) \hfill \textnormal{Chicago, IL}}
\subsection{Bachelor of Science in Computer Science \hfill \textnormal{December 2022}}
\vspace{-0.5em}
% \textit{\textbf{Bachelor of Science in Computer Science} \hfill December 2022}
\textit{\textbf{University of Illinois Chicago (UIC)} \hfill Chicago, IL}
% \\ % new line character in LaTeX
% maybe doesn't matter as much cus related to grades... \textbf{Awards:} Dean's List, \textit{January 2019 -- May 2021}


\section{Experience}
\subsection{Electrical Root Cause and Launch Support Engineer \hfill \textnormal{May 2024 -- November 2024}}
\vspace{-0.5em}
\textit{Stellantis (formerly Fiat Chrysler Automobiles) \hfill Auburn Hills, MI}
\\
$\bullet$ Performed root cause analysis and troubleshooting on all stages of the vehicle development process for 2024 EV vehicle programs for the Jeep \& Dodge brands.
\\
$\bullet$ Provided direct and remote support at development labs, assembly plants, pilot build areas, and vehicle yards.
\\
$\bullet$ Determined root cause by analyzing DTCs using CDA (Chrysler Diagnostic Application) and captured network logs using Vector CANalyzer + Vector network interface (CAN/LIN/Ethernet).
\\
$\bullet$ Verified vehicle wiring schematics and network topologies to root cause electrical issues and wrote tickets to triage issues.
\\
$\bullet$ Tested, flashed, and configured new vehicle software; verified and validated vehicle functionality.
\vspace{-0.5em}

% \subsection{Electronic Visualization Laboratory, UIC \hfill \textnormal{Chicago, IL}}
\subsection{Undergraduate Researcher \hfill \textnormal{May 2022 -- June 2022}}
\vspace{-0.5em}
% \textit{Undergraduate Researcher \hfill May 2022 --- June 2022}
\textit{Electronic Visualization Laboratory, UIC \hfill Chicago, IL}
\\
$\bullet$ Assisted with researching APIs to connect a Unity data visualization project to the web that's interfaceable with mixed reality.
\\
$\bullet$ Developed code using C\#, JavaScript, and WebXR to interface a Unity program to a web application instance.
\\
$\bullet$ Presented work and findings at weekly meetings to the research team for learning and feedback on project.
\vspace{-0.5em}

% \subsection{Technology Solutions, UIC \hfill \textnormal{Chicago, IL}}
\subsection{IT Support Specialist \hfill \textnormal{January 2020 -- December 2021}}
\vspace{-0.5em}
% \textit{IT Support Specialist \hfill January 2020 --- December 2021}
\textit {Technology Solutions, UIC \hfill Chicago, IL}
\\
$\bullet$ Assisted network engineers with troubleshooting and maintaining Cisco switches and access points throughout the campus network.
\\
$\bullet$ Provided on-site support regarding network issues to 100+ buildings (research labs, dorms, lecture halls, etc.)
\\
% $\bullet$ Managed a ticketing system (TeamDynamix) for network issues and resolved at least 3-5 support tickets per shift.
$\bullet$ Managed a ticketing system (TeamDynamix) for network issues and resolved at least 7-10 support tickets per week.
\\
$\bullet$ Maintained and contributed to engineering documentation of university's computer network to enhance troubleshooting efforts.


\section{Projects}
% \subsection{\href{https://github.com/IanLulu/MyTetris}{\underline{MyTetris}} (Personal Project) \hfill \textnormal{Java, Maven, Git}}
% \vspace{-0.5em}
% \textit{A recreation of the classic game \hfill October 2023 --- Present}
% \\
% $\bullet$ Coded and designed my version of the Tetris game in Java using its graphics libraries and object-oriented design.
% \\
% $\bullet$ Created a working demo of the game that runs on macOS.
% \\
% $\bullet$ Exploring possibility of publishing online and hosting playable game demo on sites like \url{itch.io}.
% \vspace{-0.5em}
%
\subsection{Web Development Portfolio (Personal Project) \hfill \textnormal{June 2023 -- Present}}
\vspace{-0.5em}
\textit{My \href{https://github.com/IanLulu/neocities-website}{\underline{personal}} \& \href{https://github.com/IanLulu/ianlulu.github.io}{\underline{portfolio}} websites \hfill HTML, CSS, JavaScript}
\\
$\bullet$ Developed and designed a personal website and a portfolio website using HTML, CSS, and JavaScript.
\\
$\bullet$ Published and hosted personal website on \url{neocities.org}; has garnered over 12,000+ visits alone.
\\
$\bullet$ Planning on implementing web frameworks and JavaScript libraries to improve the look, feel, and functionality of both websites.
\vspace{-0.5em}

\subsection{\href{https://github.com/uic-cs418/cs418-spring22-the-wild-card}{\underline{Impact of COVID-19}} (UIC Course Project) \hfill \textnormal{January 2022 -- May 2022}}
\vspace{-0.5em}
\textit{Data science group project \hfill Python, Jupyter Notebook, pandas, NumPy, Matplotlib}
\\
$\bullet$ Collaborated in a four-person team to analyze the impact of vaccines on COVID-19 cases.
\\
$\bullet$ Utilized various Python libraries to perform data analysis on COVID-19 datasets provided by WHO to synthesize a data report.
\\
$\bullet$ Hosted team meetings over Discord and developed data visualizations on the WHO datasets.
\\
$\bullet$ Presented the data report to entire class and answered questions from other students regarding the project.


\section{Skills}
\textbf{Programming Languages:} C, C++, Java, C\#, Python, JavaScript, HTML, CSS, SQL, {\LaTeX}, MATLAB, R, Scala, F\#
\\
\textbf{Frameworks \& Libraries:} JUnit, Node.js, React, TCP/IP; pandas, NumPy, Matplotlib, CAN/LIN
\\
\textbf{Developer Tools:} Git, VS Code, Eclipse, IntelliJ, Visual Studio, Bash, CLI, Jupyter Notebook, Google Cloud Platform, Docker
\\
\textbf{Software:} Linux, macOS, Microsoft Windows, Adobe Photoshop, Adobe Illustrator, Adobe Premiere Pro, Autodesk Inventor
\\
\textbf{Hardware:} Soldering, Arduino/Breadboard wiring, Additive/Subtractive manufacturing, Welding
\\
\textbf{Certifications:} Networking Foundations: Networking Basics -- LinkedIn, \textit{February 2020}


% cutting this section for now cus no space T^T
%
% \section{Extracurricular Activities}
% \subsection{Society of Automotive Engineers (SAE), UIC \hfill \textnormal{Chicago, IL}}
% \vspace{-0.5em}
% \textit{Baja Team Member \hfill August 2021 --- May 2022}
% \\
% $\bullet$ Assisted in the maintenance and repair of UIC SAE's off-road Baja car.
% \\
% $\bullet$ Participated in the organization's welding and machine tools workshops to obtain skills for working on the automotives.
% \\
% $\bullet$ Selected to participate in the winter off-roading competition \href{https://baja.mtu.edu/}{\underline{Blizzard Baja}} 2022 at Michigan Tech.
% \\
% $\bullet$ Selected as one of the drivers for the endurance race at the competition.
% \\
% % combined the 2/two bullets above ^
% $\bullet$ Selected as a driver in the winter off-roading competition \href{https://baja.mtu.edu/}{\underline{Blizzard Baja}} 2022 at Michigan Tech.


\end{document}